Open Set Logo Detection and Retrieval

### 2017-10-27 paper-final.tex
Prepared camera ready version.

One challenge for training a general purpose logo detector lies in appropriate training data. Many logo or trademark datasets~\cite{eakins1998,hoi2015,tursun2017} only contain the original logo graphic but no in-the-wild occurrences of these logos which are required for the target application. The need for annotated logo bounding boxes in the images limits the number of suitable available datasets. Existing logo datasets~\cite{joly2009,kalantidis2011,romberg2011,letessier2012,bianco2015,su2016,bianco2017} with available bounding boxes are often restricted to a very small number of brands and mostly high quality images. Especially, occlusions, blur and variations within a logo type are only partially covered.
To address these shortcomings, we collect the novel Logos in the Wild dataset and make it publicly available~\footnote{\url{url://to.come}}.

@@

\subsubsection*{Baseline}
\vspace*{-2.5mm}
Faster R-CNN consists of two stages, the first being an \ac{RPN} to detect object candidates in the feature maps and the second being classifiers for the candidate regions. While the second stage sharply classifies the trained brands, the \ac{RPN} will generate candidates that vaguely resemble any of the brands which is the case for many other logos. Thus, it provides an indicator whether a region of the image is a logo or not. The trained \ac{RPN} and the underlying feature extractor network are isolated and employed as a baseline open set logo detector.

\subsubsection*{Brand Agnostic}
\vspace*{-2.5mm}
The \ac{RPN} strategy is by no means optimal because it obviously has a bias towards the pre-trained brands and also generates a certain amount of false positives.
Therefore, another option to detect logos is suggested which we call the brand agnostic Faster R-CNN. It is trained with only two classes: background and logo. We argue that this solution which merges all brands into a single class yields better performance than the \ac{RPN} detector because of two reasons. 
First, in the second stage, fully connected layers preceding the output layer serve as strong classifiers which are able to eliminate false positives.
Second, these layers also serve as stronger bounding box regressors improving the localization precision of the logos.

@@

%
\setlength{\frameSize}{3.7cm}
\begin{figure*}%
\centering%
\includegraphics[height=\frameSize]{img/sample2.png}
\hfill
\includegraphics[height=\frameSize]{img/sample12.png}
\hfill
\includegraphics[height=\frameSize]{img/sample3.png}%
\\
\vspace{1.5mm}%
\includegraphics[height=\frameSize]{img/sample15.png}
\hfill
\includegraphics[height=\frameSize]{img/sample5.png}
\hfill
\includegraphics[height=\frameSize]{img/sample9.png}
\caption{Examples from the collected Logos in the Wild dataset.}%
\label{fig:logoSamples}
\end{figure*}%
%
\section{\uppercase{Logo Dataset}}
\noindent To train the proposed logo detector and feature extractor, a novel logo dataset is collected to supplement publicly available logo datasets. A comparison to other public in-the-wild datasets with annotated bounding boxes is given in table~\ref{tab:logoDatasets}.
The goal is an in-the-wild logo dataset with images including logos instead of the raw original logo graphics. In addition, images where the logo represents only a minor part of the image are preferred. See figure~\ref{fig:logoSamples} for a few examples of the collected data.
Following the general suggestions from \cite{bansal2017}, we target for a dataset containing significantly more brands instead of collecting additional image samples for the already covered brands. This is the exact opposite strategy than performed by the Logos-32plus dataset.
Starting with a list of well-known brands and companies, an image web search is performed. Because most other web collected logo datasets mainly rely on Flickr, we opt for Google image search to broaden the domain. Brand or company names are searched directly or in combination with a predefined set of search terms, \xeg, `advertisement', `building', `poster' or `store'. 
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 9cm 0cm 0cm, clip]{img/annotatedSample.pdf}%
\caption{Annotations differentiate between textual and graphical logos.}%
\label{fig:annotatedSample}
\end{figure}%
%

@@

\section{\uppercase{Experiments}}
%\noindent- explain FROC curve \\
%- maybe introduce mAP \\
%- explain baseline method(s) \\
%concepts/desired experiments \\
%- train on public non-Flickr brands \\
%- additionally train on own logo dataset \\
%- test on FlickrLogos-32 test datasets \\
%
%- additional evaluation on own SportsLogos dataset and qualitative results \\
\noindent The proposed method is evaluated on the test set benchmark of the public FlickrLogos-32 dataset including the distractors. Additional application specific experiments are performed on an internal dataset of sports event TV broadcasts. 
The training set consists of two parts. The union of all public logo datasets as listed in table~\ref{tab:logoDatasets} and the novel \ac{LitW} dataset. For a proper separation of train and test data, all brands which are present in the FlickrLogos-32 test set are removed from the public and \ac{LitW} data. Ten percent of the remaining images are set aside for network validation in each case. This results in the final training and test set sizes listed in table~\ref{tab:trainTestStatistics}.
%
\begin{table}[t]
\centering
\begingroup	
\setlength{\tabcolsep}{6pt}
\caption{Train and test set statistics.}
\label{tab:trainTestStatistics}
\begin{small}
% Table generated by Excel2LaTeX from sheet 'Tabelle1'
\begin{tabular}{cl|cc}
\textbf{phase} & \multicolumn{1}{c|}{\textbf{data}} & \multicolumn{1}{c}{\textbf{brands}} & \multicolumn{1}{c}{\textbf{RoIs}} \bigstrut[b]\\
\hline
\multirow{2}[2]{*}{train} & public & 47    & 3,113 \bigstrut[t]\\
      & public+\ac{LitW} v1.0 & 632   & 18,960 \bigstrut[b]\\
\hline
test  & FlickrLogos-32 test & 32    & 1,602 \bigstrut[t]\\
\end{tabular}%
\end{small}
\endgroup
\end{table}

In the first step, the detector stage alone is assessed. Then, the combination of detection and comparison for logo retrieval is evaluated. 
Detection and matching performance is measured by the \ac{FROC} curve~\cite{miller1969} which denotes the detection or detection and identification rate versus the number of false detections.

In all cases, the \acp{CNN} are trained until convergence. Due to the diversity of applied networks and differing dataset sizes, training settings are numerous and optimized in each case with the validation data. Convergence occurs after 200 to 8,000 training iterations with a varying batch-size of 1 for the Faster R-CNN detector, 7 for the DenseNet161, 18 for the ResNet101 and 32 for the VGG16 training due to GPU memory limitation.

@@

%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 7.4cm 0cm 0cm, clip]{img/classificationFroc.pdf}%
\caption{Detection+Classification FROC curves for the FlickrLogos-32 test set. Including dashed indicators for one standard deviation. DenseNet results are omitted for clarity, refer to table~\ref{tab:mapFlickr} for full results.}%
\label{fig:classificationFroc}
\end{figure}%
%
\subsubsection*{FlickrLogos-32}
\vspace*{-2.5mm}
In ten iterations, each of the ten FlickrLogos-32 train samples for each brand serves as query sample. This allows to assess the statistical significance of results similar to a 10-fold-cross-validation strategy. Figure~\ref{fig:classificationFroc} shows the FROC results for the trained networks including indicators for the standard deviation of the measurements. The detection identification rate denotes the amount of ground truth logos which are correctly detected and are assigned the correct brand.
While the baseline method is only able to find a minor amount of the logos, our best performing approach is able to correctly retrieve 25 percent of the logos if tolerating only one false alarm every 100 images.
As expected, the more recent network architectures provide better results. Also, including the \ac{LitW} data in the training yields a significant boost in performance. Specifically, the larger training dataset has a larger impact on the performance than a better network architecture.

@@

\subsubsection*{SportsLogos}
\vspace*{-2.5mm}
In addition to public data, target domain specific experiments are performed on TV broadcasts of sports events. In total, this non-public test set includes 298 annotated frames with 2,348 logos of 40 brands. In comparison to public logo datasets, the logos are usually significantly smaller and cover only a tiny fraction of the image area as illustrated in figure~\ref{fig:footballSample}. Besides perimeter advertising, logos on clothing or equipment of the athletes and TV station or program overlays are the most occurring logo types.
Overall, the results in this application scenario are slightly worse than in the FlickrLogos-32 benchmark with a drop in \map~from 0.464 to 0.354 for the best performing method, as indicated in figure~\ref{fig:classificationFrocFootball}. The baseline approach takes the largest performance hit showing that closed set approaches not only generalize badly to unseen logos but also to novel domains. In contrast, the proposed open set strategy shows a relatively stable cross-domain performance. Training with \ac{LitW} data again improves the results significantly.
%
\begin{figure*}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 0cm 0cm 0.5cm, clip]{img/football-1908719_1920_cut.jpg}%
\caption{Example football scene with small logos in the perimeter advertising.}%
\label{fig:footballSample}
\end{figure*}%

\section{\uppercase{Conclusions}}
\label{sec:conclusion}
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 8.5cm 0cm 0cm, clip]{img/classificationFrocFootball.pdf}%
\caption{Detection+Classification FROC curves for the Sports\-Logos test set, \map~is given in brackets.}%
\label{fig:classificationFrocFootball}
\end{figure}%
%
\noindent The limits of closed set logo retrieval approaches motivate the proposed open set approach. By this, generalization to unseen logos and novel domains is improved significantly in comparison to a naive extension of closed set approaches to open set configurations. 
Due to the large logo variety, open set logo retrieval is still a challenging task where trained methods benefit significantly from larger datasets. The lack of sufficient data is addressed by introduction of the large-scale Logos in the Wild dataset. Despite being bigger than all other in-the-wild logo datasets combined, dataset sizes should probably be scaled even further in the future. Adding the Logos in the Wild data in the training improves the mean average precision from 0.368 to 0.464 for open set logo retrieval on FlickrLogos-32.

@@

\vfill
\bibliographystyle{apalike}
{\small
\bibliography{Biblio}}

>>>>

One challenge for training a general purpose logo detector lies in appropriate training data. Many logo or trademark datasets~\cite{eakins1998,hoi2015,tursun2017} only contain the original logo graphic but no in-the-wild occurrences of these logos which are required for the target application. The need for annotated logo bounding boxes in the images limits the number of suitable available datasets. Existing logo datasets~\cite{joly2009,kalantidis2011,romberg2011,letessier2012,bianco2015,su2016,bianco2017} with available bounding boxes are often restricted to a very small number of brands and mostly high quality images. Especially, occlusions, blur and variations within a logo type are only partially covered.
To address these shortcomings, we collect the novel Logos in the Wild dataset and make it publicly available~\footnote{\url{http://s.fhg.de/logos-in-the-wild}}.

@@

\subsubsection*{Baseline}
%\vspace*{-2.5mm}
Faster R-CNN consists of two stages, the first being an \ac{RPN} to detect object candidates in the feature maps and the second being classifiers for the candidate regions. While the second stage sharply classifies the trained brands, the \ac{RPN} will generate candidates that vaguely resemble any of the brands which is the case for many other logos. Thus, it provides an indicator whether a region of the image is a logo or not. The trained \ac{RPN} and the underlying feature extractor network are isolated and employed as a baseline open set logo detector.

\subsubsection*{Brand Agnostic}
%\vspace*{-2.5mm}
The \ac{RPN} strategy is by no means optimal because it obviously has a bias towards the pre-trained brands and also generates a certain amount of false positives.
Therefore, another option to detect logos is suggested which we call the brand agnostic Faster R-CNN. It is trained with only two classes: background and logo. We argue that this solution which merges all brands into a single class yields better performance than the \ac{RPN} detector because of two reasons. 
First, in the second stage, fully connected layers preceding the output layer serve as strong classifiers which are able to eliminate false positives.
Second, these layers also serve as stronger bounding box regressors improving the localization precision of the logos.

@@

%
\setlength{\frameSize}{3.7cm}
\begin{figure*}%
\centering%
\includegraphics[height=\frameSize]{img/sample2.png}
\hfill
\includegraphics[height=\frameSize]{img/sample12.png}
\hfill
\includegraphics[height=\frameSize]{img/sample3.png}%
\\
\vspace{1.5mm}%
\includegraphics[height=\frameSize]{img/sample15.png}
\hfill
\includegraphics[height=\frameSize]{img/sample5.png}
\hfill
\includegraphics[height=\frameSize]{img/sample9.png}
\caption{Examples from the collected Logos in the Wild dataset.}%
\label{fig:logoSamples}
\end{figure*}%
%
\section{\uppercase{Logo Dataset}}
\noindent To train the proposed logo detector and feature extractor, a novel logo dataset is collected to supplement publicly available logo datasets. A comparison to other public in-the-wild datasets with annotated bounding boxes is given in table~\ref{tab:logoDatasets}.
The goal is an in-the-wild logo dataset with images including logos instead of the raw original logo graphics. In addition, images where the logo represents only a minor part of the image are preferred. See figure~\ref{fig:logoSamples} for a few examples of the collected data.
Following the general suggestions from \cite{bansal2017}, we target for a dataset containing significantly more brands instead of collecting additional image samples for the already covered brands. This is the exact opposite strategy than performed by the Logos-32plus dataset.
Starting with a list of well-known brands and companies, an image web search is performed. Because most other web collected logo datasets mainly rely on Flickr, we opt for Google image search to broaden the domain. Brand or company names are searched directly or in combination with a predefined set of search terms, \xeg, `advertisement', `building', `poster' or `store'. 
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 9.9cm 0cm 0cm, clip]{img/annotatedSample.pdf}%
\caption{Annotations differentiate between textual and graphical logos.}%
\label{fig:annotatedSample}
\end{figure}%
%

@@

\section{\uppercase{Experiments}}
%\noindent- explain FROC curve \\
%- maybe introduce mAP \\
%- explain baseline method(s) \\
%concepts/desired experiments \\
%- train on public non-Flickr brands \\
%- additionally train on own logo dataset \\
%- test on FlickrLogos-32 test datasets \\
%
%- additional evaluation on own SportsLogos dataset and qualitative results \\
\noindent The proposed method is evaluated on the test set benchmark of the public FlickrLogos-32 dataset including the distractors. Additional application specific experiments are performed on an internal dataset of sports event TV broadcasts. 
The training set consists of two parts. The union of all public logo datasets as listed in table~\ref{tab:logoDatasets} and the novel \ac{LitW} dataset. For a proper separation of train and test data, all brands present in the FlickrLogos-32 test set are removed from the public and \ac{LitW} data. Ten percent of the remaining images are set aside for network validation in each case. This results in the final training and test set sizes listed in table~\ref{tab:trainTestStatistics}.
%
\begin{table}[t]
\centering
\begingroup	
\setlength{\tabcolsep}{6pt}
\caption{Train and test set statistics.}
\label{tab:trainTestStatistics}
\begin{small}
% Table generated by Excel2LaTeX from sheet 'Tabelle1'
\begin{tabular}{cl|cc}
\textbf{phase} & \multicolumn{1}{c|}{\textbf{data}} & \multicolumn{1}{c}{\textbf{brands}} & \multicolumn{1}{c}{\textbf{RoIs}} \bigstrut[b]\\
\hline
\multirow{2}[2]{*}{train} & public & 47    & 3,113 \bigstrut[t]\\
      & public+\ac{LitW} v1.0 & 632   & 18,960 \bigstrut[b]\\
\hline
test  & FlickrLogos-32 test & 32    & 1,602 \bigstrut[t]\\
\end{tabular}%
\end{small}
\endgroup
\end{table}

In the first step, the detector stage alone is assessed. Then, the combination of detection and comparison for logo retrieval is evaluated. 
Detection and matching performance is measured by the \ac{FROC} curve~\cite{miller1969} which denotes the detection or detection and identification rate versus the number of false detections.
%
In all cases, the \acp{CNN} are trained until convergence. Due to the diversity of applied networks and differing dataset sizes, training settings are numerous and optimized in each case with the validation data. Convergence occurs after 200 to 8,000 training iterations with a varying batch-size of 1 for the Faster R-CNN detector, 7 for the DenseNet161, 18 for the ResNet101 and 32 for the VGG16 training due to GPU memory limitation.

@@

%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 7.4cm 0cm 0cm, clip]{img/classificationFroc.pdf}%
\caption{Detection+Classification FROC curves for the FlickrLogos-32 test set. Including dashed indicators for one standard deviation. DenseNet results are omitted for clarity, refer to table~\ref{tab:mapFlickr} for full results.}%
\label{fig:classificationFroc}
\end{figure}%
%
\subsubsection*{FlickrLogos-32}
%\vspace*{-2.5mm}
In ten iterations, each of the ten FlickrLogos-32 train samples for each brand serves as query sample. This allows to assess the statistical significance of results similar to a 10-fold-cross-validation strategy. Figure~\ref{fig:classificationFroc} shows the FROC results for the trained networks including indicators for the standard deviation of the measurements. The detection identification rate denotes the amount of ground truth logos which are correctly detected and are assigned the correct brand.
While the baseline method is only able to find a minor amount of the logos, our best performing approach is able to correctly retrieve 25 percent of the logos if tolerating only one false alarm every 100 images.
As expected, the more recent network architectures provide better results. Also, including the \ac{LitW} data in the training yields a significant boost in performance. Specifically, the larger training dataset has a larger impact on the performance than a better network architecture.

@@

\subsubsection*{SportsLogos}
%\vspace*{-2.5mm}
In addition to public data, target domain specific experiments are performed on TV broadcasts of sports events. In total, this non-public test set includes 298 annotated frames with 2,348 logos of 40 brands. In comparison to public logo datasets, the logos are usually significantly smaller and cover only a tiny fraction of the image area as illustrated in figure~\ref{fig:footballSample}. Besides perimeter advertising, logos on clothing or equipment of the athletes and TV station or program overlays are the most occurring logo types.
Overall, the results in this application scenario are slightly worse than in the FlickrLogos-32 benchmark with a drop in \map~from 0.464 to 0.354 for the best performing method, as indicated in figure~\ref{fig:classificationFrocFootball}. The baseline approach takes the largest performance hit showing that closed set approaches not only generalize badly to unseen logos but also to novel domains. In contrast, the proposed open set strategy shows a relatively stable cross-domain performance. Training with \ac{LitW} data again improves the results significantly.
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 0cm 0cm 0.5cm, clip]{img/football-1908719_1920_cut.jpg}%
\caption{Example football scene with small logos in the perimeter advertising.}%
\label{fig:footballSample}
\end{figure}%
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 8.5cm 0cm 0cm, clip]{img/classificationFrocFootball.pdf}%
\caption{Detection+Classification FROC curves for the Sports\-Logos test set, \map~is given in brackets.}%
\label{fig:classificationFrocFootball}
\end{figure}%
%

\section{\uppercase{Conclusions}}
\label{sec:conclusion}
\noindent The limits of closed set logo retrieval approaches motivate the proposed open set approach. By this, generalization to unseen logos and novel domains is improved significantly in comparison to a naive extension of closed set approaches to open set configurations. 
Due to the large logo variety, open set logo retrieval is still a challenging task where trained methods benefit significantly from larger datasets. The lack of sufficient data is addressed by introduction of the large-scale Logos in the Wild dataset. Despite being bigger than all other in-the-wild logo datasets combined, dataset sizes should probably be scaled even further in the future. Adding the Logos in the Wild data in the training improves the mean average precision from 0.368 to 0.464 for open set logo retrieval on FlickrLogos-32.

@@

%\vfill
\bibliographystyle{apalike}
{\small
\bibliography{Biblio}}
